### 2012-03-27 exam4/2.tex
problem 5

>>>>

\begin{problem}
\pts{???}

Iterators are an extremely useful concept.  In particular, they aren't
limited to iterating over the contents of data structures such as {\tt
ArrayList}s.  We can also construct iterators directly, for sequences
we are interested in.

Design the class {\tt RangeIterator}, which takes two {\tt Integer}s
as constructor arguments, and iterates over all of the {\tt Integer}s
between them, including \emph{both} end points.  {\tt RangeIterator}
must implement the {\tt Iterator} interface, given below.

\begin{verbatim}
interface Iterator<T> {
  Boolean hasNext();
  T next();
  // The Java definition of Iterator includes the remove method.
  // You do *not* need to implement remove.
}
\end{verbatim}

\begin{solution}
\begin{verbatim}
class RangeIterator implements Iterator<Integer> {
  Integer lo;
  Integer hi;

  RangeIterator (Integer lo, Integer hi) { 
    this.lo = lo; this.hi = hi; 
  }

  Boolean hasNext() { return this.lo <= this.hi; }

  Integer next() { this.lo = this.lo + 1; return this.lo - 1; }
}

// Tests
RangeIterator ri = new RangeIterator(0,2);
ri.hasNext() -> true
ri.next() -> 0
ri.next() -> 1
ri.hasNext() -> true
ri.next() -> 2
ri.hasNext() -> false
\end{verbatim}
\end{solution}
\newpage

\noindent
Recall our definition of function objects:
\begin{verbatim}
interface Function<T,U> {
  U call(T x);
}
\end{verbatim}
\noindent
Define the {\tt Square} class, which is a \verb|Function| that squares
\verb|Integer|s.

\ifrubric
\begin{solution}
\begin{verbatim}
class Square implements Function<Integer,Integer> {
  Integer call(Integer x) { return x * x; }
} 
Square s = new Square();
s.call(3) -> 9
s.call(0) -> 0
\end{verbatim}
\end{solution}
\else
\newpage
\fi

Using this interface, design and implement the {\tt MapIterator}
class, which takes a \verb|Function| and an \verb|Iterator| as
arguments, and iterates over the values produced by applying the
function to each result produced by the iterator.

\ifrubric
\begin{solution}
\begin{verbatim}
class MapIterator<T,U> implements Iterator<U> {
  Function<T,U> f;
  Iterator<T> i;
  MapIterator<T,U>(Function<T,U> f, Iterator<T> i) {
   this.f = f; this.i = i;
  }

  boolean hasNext() { return i.hasNext(); }
  U next() { return f.call(i.next()); }
}

//tests
Iterator<Integer> i = new MapIterator<Integer,Integer>(new Square(), 
                           new RangeIterator(1,5));
i.next() -> 1
i.next() -> 4
i.next() -> 9
i.hasNext() -> true

\end{verbatim}
\end{solution}
\else
\fi
\newpage

\noindent
Now design the method \verb|sumSquares|, which takes two
\verb|Integer|s, and uses the classes you've just defined, along with
a \verb|for| or \verb|while| loop, to compute the sum of the squares
of all the numbers between the given \verb|Integer|s, inclusive.

\ifrubric
\begin{solution}
\begin{verbatim}
class Test {
  Integer sumSquares(Integer a, Integer b) {
    Iterator<Integer> i = new MapIterator<Integer,Integer>(new Square(), 
                             new RangeIterator(a,b));
    Integer sum = 0;
    while (i.hasNext()) { sum += i.next(); }
    return sum;
  }
}

sumSquares(1,2) -> 5
sumSquares(0,0) -> 0
sumSquares(10,10) -> 100
\end{verbatim}
\end{solution}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
